---
title: "Markdown-Practice"
author: "Alex Koener"
date: "4/1/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Week 12 - R Markdown

This week's assignment is to create an **R Markdown**. A Markdown is a document you can make in RStudio that helps present or display what ever you can fit on the page!

*Here is the link to the [GitHub project repository](https://github.com/koeneralex/rprogramming-week12-R-Markdown).*

*Here is the link to the assignment's [blog post](https://alexrprogramming.blogspot.com/2021/04/week-12-r-markdown.html).*

*Here is the link to my website [Koener.co](http://www.koener.co).*



## What is R Markdown?

Similar to coding in HTML, there are tags you can give to writing elements and it **styles the text** exactly how the programer chooses. What separates Markdown from HTML is a programmer that is fluent in R easily accomplish similar tasks that HTML serves. Additionally, you can knit the documents into more than HTML including PDF documents, Word documents, and Shiny applications.

## Equation

[Albert Einstein's](einstein.jpeg) theory for of special relativity: 

$$E = mc^2$$

## Code and Plots!

Quick example of how Markdown displays **code and plots.**


```{r}

head(mtcars)

str(mtcars)

plot(mtcars$wt, mtcars$mpg)

```



## Blog Reflection

> Prior to this assignment I was slightly familiar with R Markdown and have been using it in my other class to display projects I have been working on. However, this assignment has helped me learn some more syntax to improve my Markdown skills! I see this being a very useful tool for school, career, and personal projects. 
